\section{Source Code Structure}
The source code follows the structure of a Spring project. ALl the code is located in the \textbf{src} folder and the distinction between the code of the application and the code of the tests performed on it is clear. The \textbf{main} folder contains the code for the back-end and the front-end of the system while the tests are in the \textbf{test} folder. All the back-end code is written in Java while the front-end code is written using Javascript, HTML and CSS.\\
The Spring configuration file is in \textbf{resources}. It manages %%%%%%%%%%%%%%%%%%%%%%
The following of this section describes more in detail the structure of back-end and front-end code.


\subsection{Back End}
The back-end code is all inside the \textbf{java} folder and it is divided into the following packages:
\begin{itemize}
	\item \textbf{controller};
	\item \textbf{model};
	\item \textbf{storageController}.\\\\
\end{itemize}

\subsection*{\textbf{Controller package}}
This package contains the following controllers:
\begin{itemize}
	\item \textbf{authenticationController};
	\item \textbf{individualController};
	\item \textbf{thirdPartyController}.\\\\
\end{itemize}
\textbf{AuthenticationController}\\
The authenticationController package is composed by the entities that manage the requests of login and sign up for both Individuals and Third parties. 
For this purpose, a pre-exisisting implementation of these functionalities using JWT has been imported and adapted to the needs of this application.\\

\textbf{IndividualController}\\
The individualController package contains the spring controller IndividualController and the spring service IndividualService.
The controller defines all the APIs to manage the functionalities provided to the Individuals and uses the service to communicates with the database reflecting the effects of the APIs' calls.\\

\textbf{ThirdPartyController}\\
The thirdPartyController package contains the spring controller ThirdPartyController and the spring services ThirdPartyService and AnonymousRequestBuilder.
The controller defines the APIs to manage the functionalities provided to the Third parties and uses the two services to communicates with the database reflecting the effects of the APIs' calls.

\subsection*{\textbf{Model package}}
This package is composed by the classes that realize the Object-relational mapping

\subsection*{\textbf{StorageController package}}
This package contains the interfaces that offer methods to perform queries on the database. All these interfaces extends the CrudRepository interface. The CrudRepository is an interface that extends Spring data Repository interface. CrudRepository provides generic CRUD operation on a repository for a specific type. It has generic methods for CRUD operation. 

\subsection{Front End} 
The code for the front-end is located in \textbf{resources} in the \textbf{static} folder. Here, a distinction between the code for Individuals and Third parties is made. The \textbf{individual} folder contains the CSS and Javascript files and HTML pages that are responsible for the Individualsì mobile application. CSS and html are optimized for the mobile version of the application, visualizing the same pages in large screens could present layout problems.
The \textbf{thirdParty} folder is the corresponding one for the Third parties web application.
