\section{Implemented requirements}

In this section we describe the implemented functionalities with reference to the requirements outlined in the RASD document.\\
The requirement with their reference number green are the ones available in the current implementation, the others are in red.

\subsection{Third Party Registration}
\begin{itemize}
	\item {\color{ProcessBlue}\textbf{[R.15]}} Two different users cannot have the same username.
	\item {\color{ProcessBlue}\textbf{[R.16]}} The system must allow the third party to register to the application, by specifying its VAT registration number and a password.
\end{itemize}
\subsubsection*{Database}
The database stores the User information and credentials inside the table denominated 'users'.\\
Passwords are stored as salted hashes for security purposes.

\subsubsection*{Back-end}


\subsubsection*{Front-end}
The homepage of the client application for a Guest contains a registration section showing a form to fill with registration information. The client application validates the information, performs the request to the server and shows the response.

\subsection{Individual Registration}
\begin{itemize}
	\item {\color{ProcessBlue}\textbf{[R.12]}} The individual must provide their personal data to the application during the registration process, SSN (or fiscal code) included. 
	\item {\color{ProcessBlue}\textbf{[R.13]}} The system must allow the individual to register to the application by selecting a username and a password. 
	\item {\color{ProcessBlue}\textbf{[R.15]}} Two different users cannot have the same username.
\end{itemize}
\subsubsection*{Database}
The database stores the User information and credentials inside the table denominated 'users'.\\
Passwords are stored as salted hashes for security purposes.

\subsubsection*{Back-end} 

\subsubsection*{Front-end}
The homepage of the client application for a Guest contains a registration section showing a form to fill with registration information. The client application validates the information, performs the request to the server and shows the response.


\subsection{Third Party Login}
\begin{itemize}
	\item {\color{ProcessBlue}\textbf{[R.17]}} The system must allow the third party to log in to the application by providing the combination of a VAT registration number and a password that match an account.
\end{itemize}
\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}
The homepage of the application contains (if the User is not logged in) a login form. The client application validates the information, performs the request to the server and shows the response.

\subsection{Individual Login}
\begin{itemize}
	\item {\color{ProcessBlue}\textbf{[R.14]}} The system must allow the individual to log in to the application by providing the combination of a username and a password that matches an account.
\end{itemize}
\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}
The homepage of the application contains (if the User is not logged in) a login form. The client application validates the information, performs the request to the server and shows the response.

\subsection{Individual Data Manager}

\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}

\subsection{Individual Notifications}

\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}

\subsection{Individual Settings Management}
\begin{itemize}
	\item {\color{ProcessBlue}\textbf{[R.32]}} The system must allow the individual to change his/her password.
\end{itemize}
\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}

\subsection{Individual SOS Call}

\subsubsection*{Front-end}

\subsection{Third Party Notifications}

\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}

\subsection{Third Party Settings Management}
\begin{itemize}
	\item {\color{ProcessBlue}\textbf{[R.33]}} The system must allow the Third party to change its password.
\end{itemize}
\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}

\subsection{Third Party Individual Request}

\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}

\subsection{Third Party Anonymous Request}

\subsubsection*{Database}


\subsubsection*{Back-end}


\subsubsection*{Front-end}

 
